\TheTitle

### 2016-04-22 linvis.tex
Editing Design section

In this section, we describe the progression of our tool design, showing the
benefits and drawbacks of each component.

@@

The first tool we implemented was a small command-line shell (figure
\ref{fig:shell}) that allows users to navigate through the commits and merges rather
than files and directories. The shell design permitted a user to move through merges
like they would through directories with the \verb|cd| and \verb|ls| commands. Users
can use the \verb|cat| command to see the log preview, or the \verb|more| command to
see the preview and how many lines were added and removed from the files in the
commit.

@@

The shell does not meet our design goals. It only provides users with the ability to
navigate from the root. If there is a commit or merge that they would like to
investigate, they must find it with another tool and navigate through the tree to
find it. Furthermore, it does not aggregate information in the merges, so users must
manually aggregate the metadata. Another issue with this design is that it presents
the users with the commit hashes, which are quite long and unpleasant to remember
type into the shell, but also do not provide any quick explanation of what the
commit or merge may contain.

@@

We replace the command-line interface with a web-based tool. Creating a web-based
tool enables users to use the system without having to install software or carry a
large database, making it more accessible, more easily maintainable, and platform
independent. A web-based tool can utilize more interactive means of navigation and
provide better explanations of commits and merges than the command-line interface.

@@

Searching allows a user to filter commits and merges that are irrelevant.  The
search mechanism breaks down the results by release version. A user can further
narrow down the search range using the commit date range. The commit date refers to
the date of the creation of the top-level merge. Commits and merges that are
returned may have a commit date beyond the given range if they were merged to a
top-level merge that is within the date range. A user may then provide a search
text, filtering on the author name, the commit id, or keyword from the log. Any part
of the author name may show up in the results, including searching by email address.
The commit ID must be specified from the first character to the last character. For
example, the commit `c267548755a184ef97301071300c1739a564e135' is returned when the
user searches for a commit id of `c26' in the 3.10 Linux kernel. We will use this
commit for showing each of the features of the tool.

@@

The second tab is the files tab. This tab provides information on what files have
been edited, how many lines were added, and how many lines were removed in a given
commit. This functionality is similar to the other tools available. Our tree-based
design model allows us to extend this functionality to merges, which the other tools
are unable to show. When a file is edited multiple times from different commits
within a merge, we simply add the added and removed lines to the values already
stored.

@@

The modules tab shows the modules that are contained within the commit. Modules are
not natively recognized by git, and are not going to be present in all repositories.
In the Linux repository, authors put the module they are working on in the one-line
preview of the log-message. We heuristically extract the module by taking all text
in the log preview of commits until the first colon.  Modules are logical partitions
of the information in the kernel. Depending on where the author was working, modules
can be general, such as ``bluetooth'' and ``wireless'', or can be quite specific for
individual hardware, such as ``ath9k\_hw'' and ``wl1251''. Like files, we are able
to show what modules are edited in merges and commits. The image in figure
\ref{fig:modules} shows the modules for a commit. A commit will only ever have one
module that it is associated with.

@@

The tree view is what makes this tool unique to other tools, providing a full view
of the entire merge tree. We have experimented with various types of trees; list
trees are similar to the representation by many file system explorers,
Reingold-Tilford trees which clearly represent the tree structure, and bubble trees
which organize the data hierarchically by having the parent node contain the child
nodes.

@@

The list tree  viewer is in the form of nested lists, and is designed to more
closely model the tree hierarchy view found in file browsers. This tree only
contains the commits and merges that are within the subtrees of the current merge. A
commit will never have any items in this tree, as it is a leaf. To accompany the
tree, we include breadcrumbs at the top of the page to enable a user to navigate
both from the root to the leaves and from a leaf to the root. The last item in the
breadcrumb list is the current commit, the next item is the parent of the current
commit, and the first item is the root merge into the kernel.

@@

The bubble tree provides a very clear picture of where a commit is located in the
hierarchy. The currently selected commit or merge is colored red, while non-selected
merges use a blue color and commits use white. The depth of the blue colouring is
dependent on how deep in the hierarchy that node is. The root is the lightest blue,
and the contained merges are progressively darker.

>>>>

We came up with two designs. We recognized that the structure of the repository was
similar to the wide and shallow tree-structure of a file system. We began with a
command-line shell interface. Then transitioned to a web-based tool where we looked
beyond the file system structure. In this section, we describe the progression of
our tool design, showing the benefits and drawbacks of each component.

@@

The first tool we implemented was a small command-line shell (figure
\ref{fig:shell}) that allows users to navigate through the commits and merges as one
might navigate through files and directories. A user could navigate toward the
leaves of the tree by using the \verb|cd| command followed by the commit id of the
next merge. The user could then navigate toward the root by issuing \verb|cd ../|,
as they would in a file system. Users can use \verb|ls| to view what commits and
merges exist in the current working merge, then use \verb|cat| to view the log
preview of a commit or \verb|more| to see the preview and how many lines were added
and removed from the files in the commit.

@@

The shell does not meet our design goals. It only provides users with the ability to
navigate from the root. If there is a commit or merge that they would like to
investigate, they must find it with another tool and navigate through the tree to
find it. Furthermore, it does not aggregate information in the merges, so users must
manually aggregate the metadata. Another issue with this design is that it presents
the users with the commit hashes, which are quite long and unpleasant to remember
and type into the shell, but also do not provide any quick explanation of what the
commit or merge may contain.

@@

We replace the command-line interface with a web-based tool. Creating a web-based
tool enables users to use the system without having to install additional software
or carry a large database, making it more accessible, more easily maintainable, and
platform independent. A web-based tool can utilize more interactive means of
navigation and provide better explanations of commits and merges than the
command-line interface.

@@

Searching allows a user to filter commits and merges that are irrelevant. The search
mechanism breaks down the results by release version. A user can further narrow down
the search range using the commit date range. The commit date refers to the date of
the creation of the top-level merge. The commits and merges that are returned may
have a commit date beyond the given range if they were merged by Linus within the
date range. A user may then provide a search text, filtering on the author name,
the commit id, or keyword from the log. Any part of the author name may show up in
the results, including searching by email address. The commit ID must be specified
from the first character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches for a
commit id of `c26' in the 3.10 Linux kernel. We will use this commit for showing
each of the features of the tool.

@@

The second tab is the files tab. This tab provides information on what files have
been edited, how many lines were added, and how many lines were removed in a given
commit. This functionality is similar to the other tools available. Our tree-based
design model allows us to extend this functionality to merges, which the other tools
are unable to show. When a file is edited multiple times from different commits
within a merge, we simply add the added and removed lines to the values already
stored, though this could be extended to use the diff information to determine when
a line has been replaced rather than incrementing the lines removed and the lines
added.

@@

The modules tab shows the modules that are contained within the commit. Modules are
not natively recognized by git, and are not going to be present in all repositories.
In the Linux repository, authors put the module they are working on in the one-line
preview of the log-message. We heuristically extract the module by taking all text
in the log preview of commits until the first colon.  Modules are logical partitions
of the information in the kernel. Depending on where the author was working, modules
can be general, such as ``bluetooth'' and ``wireless'', or can be quite specific for
individual hardware, such as ``ath9k\_hw'' and ``wl1251''. In a few cases, the
author of a commit does not correctly follow this format and the hueristic approach
fails. Like files, we are able to show what modules are edited in merges and
commits. The image in figure \ref{fig:modules} shows the modules for a commit. A
commit will only ever have one module that it is associated with, merges with more
than one child will have more.

@@

The tree view is what makes this tool unique to other tools, providing a full view
of the entire merge tree. We have experimented with various types of trees; list
trees are similar to the representation used in many file system explorers,
Reingold-Tilford trees clearly represent the tree structure, and bubble trees
organize the data hierarchically by having the parent node contain the child nodes
similarly to tree maps, but clearly showing the parent-child relationships between
nodes.

@@

The list tree viewer is in the form of nested lists, and is designed to more closely
model the tree hierarchy view found in file browsers. This tree only contains the
commits and merges that are within the subtrees of the current merge. A commit will
never have any items in this tree as it is a leaf. To accompany the tree, we include
breadcrumbs at the top of the page to enable a user to navigate both from the root
to the leaves and from a leaf to the root. The last item in the breadcrumb list is
the current commit, the previous item is the parent of the current commit, and the
first item is the root merge into the kernel.

@@

The bubble tree provides a very clear picture of where a commit is located in the
hierarchy. The currently selected commit or merge is colored red, while non-selected
merges use a shade of blue and commits use white. The depth of the blue colouring is
dependent on how deep in the hierarchy that node is. The root is the lightest blue,
and the contained merges are progressively darker.
